\Title

### 2021-01-07 manuscript/manuscript.tex
Start review of depths of sources section
Just moved a few things around but still need to revise the actual text.
Will do an enumerate to make it more similar to the horizontal layouts
section.

The depth of the point sources can be chosen following different criteria.
Deep sources generate low frequencies, while shallow ones generate high
frequencies (cite).
The simplest option is to locate all sources at the same depth, which we will
call \emph{constant depth} in the future (see Fig.~\ref{fig:depth-types}(a)).
If the measurement were taken at significantly different altitudes, the
elevated computation points will be more distant to the sources than the lower
ones.
This may create problems on reproducing high frequencies on the elevated
points.

One possible solution is to locate each source below its corresponding
observation (or block averaged) point at a constant \emph{relative depth}
from it.
The depth of each source can be computed as the height of its corresponding
observation (or block averaged) point minus a depth parameter that assumes the
same value for all sources (see Fig.~\ref{fig:depth-types}(b)).
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation (or block averaged) point.

In case our survey presents heavily clustered data points on some areas, we may
want the sources below that region to be shallower in order to reproduce the
high frequencies measured by these clustered observation points.
We can propose a \emph{variable depth} approach: it locates each point source
according to the \emph{relative depth} and then subtracts a term proportional
to the mean distance to its $k$ nearest neighbour sources
(see Fig.~\ref{fig:depth-types}(c)).
So, the depth of the sources can be computed as follows:

@@

Similar approaches for setting sources at depths that depend
on the distance to their nearest neighbours were already proposed by
\citet{cordell1992, guspi2004, guspi2009}.

@@

>>>>

It is widely known from potential theory that the depth of a point source
influences the wavelength of the observed field at the surface.
This makes the source depth a key parameter affecting the outcome of
interpolation and other operations done with equivalent sources.
Several different strategies for assigning the depths of equivalent sources
have been proposed in the literature.

\begin{enumerate}
  \item
The simplest option is to locate all sources at the same depth, which we will
call \emph{constant depth} in the future (see Fig.~\ref{fig:depth-types}(a)).
If the measurement were taken at significantly different altitudes, the
elevated computation points will be more distant to the sources than the lower
ones.
This may create problems on reproducing high frequencies on the elevated
points.
 \item
One possible solution is to locate each source below its corresponding
observation (or block averaged) point at a constant \emph{relative depth}
from it.
The depth of each source can be computed as the height of its corresponding
observation (or block averaged) point minus a depth parameter that assumes the
same value for all sources (see Fig.~\ref{fig:depth-types}(b)).
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation (or block averaged) point.
 \item
In case our survey presents heavily clustered data points on some areas, we may
want the sources below that region to be shallower in order to reproduce the
high frequencies measured by these clustered observation points.
We can propose a \emph{variable depth} approach: it locates each point source
according to the \emph{relative depth} and then subtracts a term proportional
to the mean distance to its $k$ nearest neighbour sources
(see Fig.~\ref{fig:depth-types}(c)).

So, the depth of the sources can be computed as follows:

@@

Similar approaches for setting sources at depths that depend
on the distance to their nearest neighbours were already proposed by
\citet{cordell1992, guspi2004, guspi2009}.
\end{enumerate}

@@

We will test each of these strategies on synthetic data to evaluate their
effectiveness.
